\documentclass[letterpaper,11pt]{article}

  \usepackage{latexsym}
  \usepackage[empty]{fullpage}
  \usepackage{titlesec}
  \usepackage{marvosym}
  \usepackage[usenames,dvipsnames]{color}
  \usepackage{verbatim}
  \usepackage{enumitem}
  \usepackage[]{hyperref}
  \usepackage{fancyhdr}
  
  
  \pagestyle{fancy}
  \fancyhf{} % clear all header and footer fields
  \fancyfoot{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
  
  
  % Adjust margins
  \addtolength{\oddsidemargin}{-0.375in}
  \addtolength{\evensidemargin}{-0.5in}
  \addtolength{\textwidth}{1in}
  \addtolength{\topmargin}{-.5in}
  \addtolength{\textheight}{1.0in}
  
  \urlstyle{same}
  
  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}
  
  % Sections formatting
  \titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
  
  %-------------------------
  % Custom commands
  \newcommand{\resumeItem}[2]{
    \item\small{
      \textbf{#1}{: #2 \vspace{-2pt}}
    }
  }
  
  \newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
      \end{tabular*}\vspace{-5pt}
  }
  
  \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
  
  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet]}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
  
  %-------------------------------------------
  %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
  
  \begin{document}
  
  %----------HEADING-----------------
  \textbf{\Huge Ruiyang Wang}
  \newline \newline
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    Looking for Full-time job for May 2019 & 
    \href{mailto:rywang014@gmail.com}{rywang014@gmail.com} \\
    1075 Space Park Way SPC 118, Mountain View, CA 94043  & (669) 215-9946 \\
  \end{tabular*}
  
  
  %-----------EDUCATION-----------------
  \section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Carnegie Mellon University}{Mountain View, CA}
  {Master of Science in Software Engineering}{May 2019}
  \resumeSubheading
  {Shanghai Jiao Tong University}{Shanghai, China}
  {Bachelor of Science in Computer Science}{June 2017}
  \resumeSubHeadingListEnd
  
  
  %
  %--------PROGRAMMING SKILLS------------
  \section{Skills}
  \resumeSubHeadingListStart
  \resumeSubItem{Languages}
  {C++11/14, Python, C, Java, JavaScript, HTML, Rust, Objective-C, Swift, C\#}
  \resumeSubItem{Technologies}{Kubernetes, Docker, Kafka, Redis, MongoDB, PostgresSQL, MapReduce, Spark, HBase}
  \resumeSubItem{Skills}{Microservices, Cloud Computing, High performance C++ applications, CI/CD workflow}
  
  \resumeSubHeadingListEnd
  
  %-----------EXPERIENCE-----------------
  \section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
  {Clarity Movement Co., Software Team, SDE Intern}{}
  {Constructed automated microservice documentation, monitoring and orchestration}{May 2018 - Aug 2018}
  \resumeItemListStart
  \resumeItem{Document Generation} {Designed CI program to update documents from code for reliable lookup and testing.}
  \resumeItem{Microservice Monitoring}{Traced requests and performances of microservices in \textbf{Node.JS} and \textbf{Python} on AWS Lambda and AWS Elastic Beanstalk with AWS X-Ray integration.}
  \resumeItem{Microservice Orchestration}
  {Speedup integration testing \textbf{2x} by creating orchestration tool based on \textbf{Kubernetes} for \textbf{MongoDB}, \textbf{Kafka}, \textbf{Redis} and business microservices for fast, \textbf{dockerized} testing and deploying}
  \resumeItemListEnd
  
  \resumeSubheading
  {YITU Tech, Infrastructure Team, SDE Intern}{}
  {Accelerated Machine Learning Training and Inference}{Sep 2017 - Dec 2017}
  \resumeItemListStart
  \resumeItem{Dataset Service for Machine Learning}
  {Accelerated PyTorch jobs \textbf{3x} by designing and implementing distributed high-performance key-value dataset service.}
  \resumeItem{C++ Medical Imaging Data Service}
  {Achieved \textbf{5x} speed for medicine imaging storage service with high availability and conformance to industrial standards by reimplementing critical logic.}
  \resumeItemListEnd
  
  \resumeSubheading
  {Microsoft, Azure China Marketplace Team, SDE Intern}{} % should I just left it blank?
  {Developed user-friendly online marketplace to purchase and deploy images to Azure China}{June 2016 - Sep 2016}
  \resumeItemListStart
  \resumeItem{Azure Cloud Computing}
  {Developed \textbf{Azure China Marketplace} selling and deploying images to Azure.}
  \resumeItem{Full Stack Web Development}
  {Built extensible and flexible website with \textbf{C\#}, \textbf{HTML}, \textbf{CSS} and \textbf{JavaScript}.}
  \resumeItem{Test driven development}
  {Conducted TDD consistently to reduce \textbf{50\%} bugs in production.}
  \resumeItemListEnd
  
  \resumeSubHeadingListEnd
  
  
  %-----------PROJECTS-----------------
  \section{Projects}
  \resumeSubHeadingListStart
  
  \resumeSubheading{\href{https://github.com/xplorld/MongoDBClusterOnDocker}{Docker Image of MongoDB Cluster}}{}
  {Dockerized MongoDB cluster for integration testing}{May 2018 - Aug 2018}
  \resumeItemListStart
  \resumeItem{Fast Initialization}
  {Created lightweight container initializing the whole cluster in seconds.}
  \resumeItem{Kubernetes Integration}
  {Enabled easy integration into Kubernetes Cluster with minimal configurations.}
  \resumeItem{Production-like Testing Environment}
  {Provided production-like database connection for accurate testing.}
  \resumeItemListEnd
  
  \resumeSubheading{Twitter Analysis Web Service}{}
  {Course project of 15619 Cloud Computing at CMU}{Jan 2018 - May 2018}
  \resumeItemListStart
  \resumeItem{On-Cloud Big Data Analysis}
  {Extracted, Transformed and Loaded \textbf{1 TB} Tweet data by \textbf{MapReduce} on \textbf{AWS} for emotional scores, retweet relations and hashtag recommendations.}
  \resumeItem{High-performance Query Service}
  {Led developing highly optimized, distributed web service with Vert.x framework in Java and load balancer for a 20000 QPS throughput while exercising fiscal control.}
  \resumeItemListEnd
  
  \resumeSubheading{Open Source Contributions}{}
  {Various microservice-related contributions}{}
  \resumeItemListStart
  \resumeItem{\href{https://github.com/uutils/coreutils/pull/1283}{uutils/coreutils}}{Cross-platform Rust rewrite of the GNU coreutils.}
  \resumeItem{\href{https://github.com/aws/chalice/pull/875}{aws/chalice}}{Python Serverless Microframework for AWS.}
  \resumeItem{\href{https://github.com/aws/aws-xray-sdk-python/pull/65}{aws/aws-xray-sdk-python}}{AWS X-Ray SDK for the Python programming language.}
  \resumeItemListEnd 
  
  \resumeSubHeadingListEnd
  
  
  %-------------------------------------------
  \end{document}
  